\documentclass[10pt,portrait]{article}
\usepackage[margin=1cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{amsmath}

\begin{document}

\small

\begin{multicols}{ 3 }
\section*{3S03 Midterm Notes}
\textbf{Ahmad Allabadi \hfill February 2025}

\section*{Module 1}
\subsection*{Testing}
\begin{itemize}
    \item \textbf{Dynamic Testing:} Execute code.
    \item \textbf{Static Testing:} No code execution. Examples:
    \begin{itemize}
        \item Code Review
        \item Requirements Review
        \item Design Review
    \end{itemize}
    \item \textbf{Black-Box Testing:} No implementation knowledge. Examples:
    \begin{itemize}
        \item Login page functionality
        \item Cart checkout functionality
    \end{itemize}
    \item \textbf{Grey-Box Testing:} Some implementation knowledge. Examples:
    \begin{itemize}
        \item Database queries
        \item API requests
    \end{itemize}
    \item \textbf{White-Box Testing:} Full implementation knowledge.
\end{itemize}

\subsection*{Functional vs Non-Functional Testing}
\begin{itemize}
    \item \textbf{Functional:} Specific function checks. Examples:
    \begin{itemize}
        \item Login Page
        \item Shopping Cart
    \end{itemize}
    \item \textbf{Non-Functional:} Beyond functionality. Examples:
    \begin{itemize}
        \item Load Testing
        \item Security Testing
    \end{itemize}
\end{itemize}

\subsection*{Fault, Error, Failure}
\begin{itemize}
    \item \textbf{Fault:} Leads to an error.
    \item \textbf{Error:} Incorrect internal state.
    \item \textbf{Failure:} Incorrect external state.
\end{itemize}

\subsection*{Testing Types}
\begin{itemize}
    \item \textbf{Unit Testing:} Smallest parts, typically white-box.
    \item \textbf{System Testing:} Whole system, often black-box.
    \item \textbf{Integration Testing:} Testing combined components.
    \item \textbf{Acceptance Testing:} Based on user needs.
    \item \textbf{Smoke Testing:} Basic functionality check.
    \item \textbf{Regression Testing:} Ensure unchanged functionality.
\end{itemize}

\section*{Module 2}
\subsection*{Testing Techniques}
\begin{itemize}
    \item \textbf{Exploratory Testing:} No predefined tests.
    \item \textbf{Specification-Based Testing:} Against specifications.
    \item \textbf{Model-Based Testing:} Against expected behavior model.
    \item \textbf{Fuzz Testing:} Random inputs.
    \item \textbf{Partition Testing:} Input domain partitioning.
    \item \textbf{Boundary Testing:} Values on domain boundaries.
\end{itemize}

\subsection*{Coverage-Based Testing}
\begin{itemize}
    \item \textbf{Statement Coverage:} Execute every statement.
    \item \textbf{Branch Coverage:} Ensure each path.
    \item \textbf{Condition Coverage:} Each condition true/false.
    \item \textbf{Path Coverage:} All independent paths.
\end{itemize}

\section*{Module 3}
\subsection*{Software Metrics}
\begin{itemize}
    \item \textbf{Exhaustive Testing:} All possible inputs.
    \item \textbf{Coverage:} Proportion of domain tested.
    \item \textbf{MC/DC:} Important combinations only.
\end{itemize}

\subsection*{Structural Testing}
\begin{itemize}
    \item \textbf{Source vs Code:} Differences in coverage.
    \item \textbf{Criteria Subsumption:} One criterion implies another.
\end{itemize}

\section*{Module 4}
\subsection*{Reviews and Analysis}
\begin{itemize}
    \item \textbf{Types of Review:}
    \begin{itemize}
        \item Ad-hoc
        \item Peer deskcheck
        \item Pair Programming
        \item Walkthrough
        \item Team Review
        \item Formal Inspection
    \end{itemize}
\end{itemize}

\subsection*{Mutation Testing}
\begin{itemize}
    \item Assume correctness, make changes, check behavior.
\end{itemize}
\end{multicols}

\end{document}