\documentclass[10pt,portrait]{article}
\usepackage[margin=1cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{amsmath}

\begin{document}

\small

\begin{multicols}{ 2 }
\section*{3S03 Midterm Notes}
\subsection*{Ahmad Allabadi, February 2025}

\section*{Module 1}

\subsection*{Testing Types}
\begin{itemize}
    \item \textbf{Dynamic Testing}: Execute code.
    \item \textbf{Static Testing}: Review code, requirements, design.
    \item \textbf{Black-Box Testing}: No implementation knowledge.
    \item \textbf{Grey-Box Testing}: Some implementation knowledge.
    \item \textbf{White-Box Testing}: Full implementation knowledge.
    \item \textbf{Functional Testing}: Check specific functionality.
    \item \textbf{Non-Functional Testing}: Assess non-functional aspects.
\end{itemize}

\subsection*{Key Concepts}
\begin{itemize}
    \item \textbf{Fault}: Potential error source.
    \item \textbf{Error}: Incorrect internal state.
    \item \textbf{Failure}: Incorrect external state.
\end{itemize}

\subsection*{Testing Levels}
\begin{itemize}
    \item \textbf{Unit Testing}: Test smallest program parts.
    \item \textbf{System Testing}: Test entire system.
    \item \textbf{Integration Testing}: Test component interactions.
    \item \textbf{Acceptance Testing}: Validate user needs.
    \item \textbf{Smoke Testing}: Quick major feature check.
    \item \textbf{Regression Testing}: Verify unchanged behavior post-modification.
\end{itemize}

\section*{Module 2}

\subsection*{Testing Strategies}
\begin{itemize}
    \item \textbf{Exploratory Testing}: Unscripted, on-the-go tests.
    \item \textbf{Specification-Based Testing}: Against specifications.
    \item \textbf{Model-Based Testing}: Against expected behavior model.
    \item \textbf{Fuzz Testing}: Random inputs.
    \item \textbf{Test Oracle}: Reference for test validation.
\end{itemize}

\subsection*{Partition Testing}
\begin{itemize}
    \item Partition input domain into equivalence classes.
    \item Types: Strong/Normal, Strong/Robust, Weak/Normal, Weak/Robust.
    \item \textbf{Boundary Testing}: Test domain boundaries.
\end{itemize}

\subsection*{Coverage Testing}
\begin{itemize}
    \item \textbf{Statement, Branch, Path Coverage}.
    \item \textbf{Fault Injection}: Introduce faults, test robustness.
\end{itemize}

\section*{Module 3}

\subsection*{Coverage Concepts}
\begin{itemize}
    \item \textbf{Exhaustive Testing}: All inputs covered.
    \item \textbf{Combinatorial Coverage}: All condition combinations.
    \item \textbf{MC/DC}: Minimal important combinations.
    \item \textbf{Source vs Code Coverage}: Ensure coverage at both levels.
\end{itemize}

\subsection*{Structural Testing}
\begin{itemize}
    \item \textbf{Criteria Subsumption}: Higher criteria cover lower.
\end{itemize}

\section*{Module 4}

\subsection*{Review and Analysis}
\begin{itemize}
    \item Types: Ad-hoc, Peer deskcheck, Pair Programming, Walkthrough, Team Review, Formal Inspection.
    \item \textbf{Mutation Testing}: Introduce syntax changes, re-test.
\end{itemize}

\subsection*{Test Doubles}
\begin{itemize}
    \item \textbf{Dummy, Fake, Stubs, Spies, Mock}.
\end{itemize}
\end{multicols}

\end{document}