\documentclass[10pt,portrait]{article}
\usepackage[margin=1cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{amsmath}

\begin{document}

\small

\begin{multicols}{ 2 }
\section*{3S03 Midterm Notes}
\subsection*{Ahmad Allabadi}
\subsection*{February 2025}

\section{Module 1}

\subsection{Testing Types}
\begin{itemize}
    \item \textbf{Dynamic Testing}: Executing code.
    \item \textbf{Static Testing}: Without execution.
    \begin{itemize}
        \item Code Review
        \item Requirements Review
        \item Design Review
    \end{itemize}
    \item \textbf{Black-Box}: No implementation knowledge.
    \item \textbf{Grey-Box}: Some implementation knowledge.
    \item \textbf{White-Box}: Full implementation knowledge.
\end{itemize}

\subsection{Testing Strategies}
\begin{itemize}
    \item \textbf{Functional Testing}: Specific functionality checks.
    \item \textbf{Non-Functional Testing}: Beyond functionality.
    \item \textbf{Unit Testing}: Smallest parts testing.
    \item \textbf{System Testing}: Whole system testing.
    \item \textbf{Integration Testing}: Component interaction testing.
    \item \textbf{Acceptance Testing}: User needs and business requirements.
    \item \textbf{Smoke Testing}: Basic functionality check.
    \item \textbf{Regression Testing}: Re-use tests post-changes.
    \item \textbf{Solitary Unit Testing}: Isolated unit tests.
    \item \textbf{Social Unit Testing}: Dependent unit tests.
\end{itemize}

\section{Module 2}

\subsection{Advanced Testing Techniques}
\begin{itemize}
    \item \textbf{Exploratory Testing}: No predefined tests.
    \item \textbf{Specification-Based Testing}: Against specifications.
    \item \textbf{Model-Based Testing}: Against expected behavior models.
    \item \textbf{Fuzz Testing}: Random inputs testing.
    \item \textbf{Test Oracle}: Determines test outcomes.
    \item \textbf{Partition Testing}: Input domain partitioning.
    \item \textbf{Boundary Testing}: Domain boundary values.
    \item \textbf{Coverage-Based Testing}: Until coverage target.
    \item \textbf{Fault Injection}: Introduce faults deliberately.
\end{itemize}

\subsection{Methodologies}
\begin{itemize}
    \item \textbf{Waterfall Method}
    \item \textbf{V-Model}
    \item \textbf{Test Driven Development (TDD)}
\end{itemize}

\section{Module 3}

\subsection{Coverage and Metrics}
\begin{itemize}
    \item \textbf{Software Metric}: Measurement system.
    \item \textbf{Exhaustive Testing}: All inputs.
    \item \textbf{Coverage Types}
    \begin{itemize}
        \item \textbf{Statement}
        \item \textbf{Branch}
        \item \textbf{Condition}
        \item \textbf{Path}
        \item \textbf{Combinatorial}
    \end{itemize}
    \item \textbf{MC/DC}: Modified Condition/Decision Coverage.
    \item \textbf{Criteria Subsumption}
\end{itemize}

\section{Module 4}

\subsection{Review and Analysis}
\begin{itemize}
    \item \textbf{Reviews}: Qualitative evaluation.
    \item \textbf{Analysis}: Repeatable evidence.
    \item \textbf{Peer Review}
    \item \textbf{Software Review}
\end{itemize}

\subsection{Types of Review}
\begin{itemize}
    \item Ad-hoc reviews
    \item Peer deskcheck
    \item Pair Programming
    \item Walkthrough
    \item Team Review
    \item Formal Inspection
\end{itemize}

\subsection{Testing Enhancements}
\begin{itemize}
    \item \textbf{Fault Injection}
    \item \textbf{Mutation Testing}
\end{itemize}
\end{multicols}

\end{document}