\documentclass[10pt,portrait]{article}
\usepackage[margin=1cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{amsmath}

\begin{document}

\small

\begin{multicols}{ 2 }
\title{3S03 Midterm Notes}
\author{Ahmad Allabadi}
\date{February 2025}

\section*{Module 1}

\subsection*{Testing Types}
\begin{itemize}
    \item \textbf{Dynamic Testing:} Executing code.
    \item \textbf{Static Testing:} Without execution. Examples:
    \begin{itemize}
        \item Code Review
        \item Requirements Review
        \item Design Review
    \end{itemize}
    \item \textbf{Black-Box Testing:} No knowledge of implementation. Examples:
    \begin{itemize}
        \item Login page functionality
        \item Cart checkout functionality
    \end{itemize}
    \item \textbf{Grey-Box Testing:} Some knowledge of implementation. Examples:
    \begin{itemize}
        \item Database query testing
        \item API requests testing
    \end{itemize}
    \item \textbf{White-Box Testing:} Full knowledge of implementation.
\end{itemize}

\subsection*{Functional vs Non-Functional Testing}
\begin{itemize}
    \item \textbf{Functional Testing:} Specific functionality checks. Examples:
    \begin{itemize}
        \item Login Page Testing
        \item Shopping cart functionality
    \end{itemize}
    \item \textbf{Non-Functional Testing:} Beyond functionality. Examples:
    \begin{itemize}
        \item Load Testing
        \item Security Testing
    \end{itemize}
\end{itemize}

\subsection*{Testing Levels}
\begin{itemize}
    \item \textbf{Unit Testing:} Smallest program parts, precise fault detection.
    \item \textbf{System Testing:} Whole system, high-level fault detection.
    \item \textbf{Integration Testing:} Testing combined units. Approaches:
    \begin{itemize}
        \item Big Bang
        \item Top-Down
        \item Bottom-Up
    \end{itemize}
\end{itemize}

\section*{Module 2}

\subsection*{Testing Approaches}
\begin{itemize}
    \item \textbf{Exploratory Testing:} No predefined tests.
    \item \textbf{Specification-Based Testing:} Against specifications.
    \item \textbf{Model-Based Testing:} Against expected behavior models.
    \item \textbf{Fuzz Testing:} Random inputs.
\end{itemize}

\subsection*{Partition and Boundary Testing}
\begin{itemize}
    \item \textbf{Partition Testing:} Input domain partitioning.
    \item \textbf{Boundary Testing:} Testing boundary values.
\end{itemize}

\subsection*{Coverage Testing}
\begin{itemize}
    \item \textbf{Statement Coverage:} Execute every statement.
    \item \textbf{Branch Coverage:} Ensure each path is taken.
    \item \textbf{Condition Coverage:} Execute conditions as True and False.
    \item \textbf{Path Coverage:} Execute every independent path.
\end{itemize}

\section*{Module 3}

\subsection*{Code Coverage}
\begin{itemize}
    \item \textbf{Structural Coverage:} Internal code structure.
    \item \textbf{Structural Testing:} Verifying internal code structure.
    \item \textbf{Criteria Subsumption:} Criterion A subsumes B if satisfying A implies satisfying B.
\end{itemize}

\section*{Module 4}

\subsection*{Review and Analysis}
\begin{itemize}
    \item \textbf{Types of Review:}
    \begin{itemize}
        \item Ad-hoc reviews
        \item Peer deskcheck
        \item Pair Programming
        \item Walkthrough
        \item Team Review
        \item Formal Inspection
    \end{itemize}
    \item \textbf{Fault Injection:} Testing by introducing faults.
    \item \textbf{Mutation Testing:} Slight changes to test syntactic elements.
\end{itemize}
\end{multicols}

\end{document}